### 2013-11-27 inst/doc/README.Rmd
updated documentation

```{r echo=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, cache=FALSE)
```

@@

```{r eval=FALSE}
library(devtools)
install_github("RNeXML", "ropensci")
```

@@

```{r}
library(RNeXML)
f <- system.file("examples", "trees.xml", package="RNeXML")
nexml <- nexml_read(f)
tr <- get_tree(nexml) # or: as(nexml, "phylo")
plot(tr[[1]])
```

>>>>

```{r echo=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, cache=TRUE)
```

@@

```{r eval=FALSE}
library(devtools)
install_github("RNeXML", "ropensci")
library(RNeXML)
```

```{r echo=FALSE}
library(RNeXML)
```

@@

```{r}
f <- system.file("examples", "comp_analysis.xml", package="RNeXML")
nexml <- nexml_read(f)
tr <- get_tree(nexml) # or: as(nexml, "phylo")
plot(tr)
```
